Stochastic Optimal Control of Single Neuron Spike Trains

### 2013-09-02 draft.tex
sec 5.2 revision

\subsection{Multi-Spike Control}
We now turn to the ultimate goal of our analysis, the control of {\sl spike
trains}. In particular, we will generate $M=10$ realizations of $N=20$ spikes
each in an attempt to meet a prescribed spike train. We will focus on two
regimes, the sub-threshold regime with either low or high noise.
The results
for parameters from the Sub-Threshold, Low-Noise regime are shown in
results in \cref{fig:targettrain_cl_lownoise,fig:targettrain_ol_lownoise}.
While, the results
for parameters from the Sub-Threshold, High-Noise regime are shown in
results in
\cref{fig:targettrain_cl_SUPT_HN,fig:targettrain_cl_SUPT_ln,fig:targettrain_ol_SUPT_ln,fig:targettrain_ol_SUPT_HN}.
%\usepackage{graphics} is needed for \includegraphics
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% SUPER-THRESHOLD REGIME LOW-NOISe:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htp]
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_ln_cl_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl closed-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,Low-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy} 
  \label{fig:targettrain_cl_SUPT_ln}
\end{center}
\end{figure}  
\begin{figure}[htp] 
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_ln_ol_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl open-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,Low-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy}
  \label{fig:targettrain_ol_SUPT_ln}
\end{center} 
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% SUPER-THRESHOLD REGIME HIGH-NOISe:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htp]
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_HN_cl_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl closed-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,High-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy}
  \label{fig:targettrain_cl_SUPT_HN}
\end{center} 
\end{figure}
\begin{figure}[htp]
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_HN_ol_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl open-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,High-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy}
  \label{fig:targettrain_ol_SUPT_HN}    
\end{center}
\end{figure}

>>>>

\subsection{Multi-Spike Control}
We now turn to the ultimate goal of our analysis, the control of {\sl spike
trains}. In particular, we will generate $M=10$ realizations of $N=20$ spikes
each in an attempt to meet a prescribed spike train. We will focus on two
regimes, the Supra-Threshold regime with either low or high noise.
The results
for parameters from the low-noise regime are shown in
results in \cref{fig:targettrain_cl_lownoise,fig:targettrain_ol_lownoise}, 
while, the results
for the high-noise regime are shown in
results in
\cref{fig:targettrain_cl_highnoise,fig:targettrain_ol_highnoise}. In all cases,
the target train is obtained by a simulation of the Supra-Threshold High Noise
regime with no additional control, i.e.\ $\a(\cdot) = 0$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% SUPER-THRESHOLD REGIME LOW-NOISe:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htp]
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_ln_cl_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl closed-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,Low-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy} 
  \label{fig:targettrain_cl_lownoise}
\end{center}
\end{figure}  
\begin{figure}[htp] 
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_ln_ol_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl open-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,Low-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy}
  \label{fig:targettrain_ol_lownoise}
\end{center} 
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% SUPER-THRESHOLD REGIME HIGH-NOISe:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htp]
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_HN_cl_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl closed-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,High-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy}
  \label{fig:targettrain_cl_highnoise}
\end{center} 
\end{figure}
\begin{figure}[htp]
\begin{center}
  \includegraphics[width=.99\textwidth]{Figs/TrainController/SUPT_HN_ol_trains_sim_10.pdf}
  \caption[ ]{How good the {\sl open-loop} controller is at hitting a target
  spike train. Uses the parameters from the Super-Threshold,High-Noise regime.
  The target spike train was generated using the model itself, with
  parameters from the Super-Threshold, High-Noise regime, without an applied
  control, $\a=0$.
  There are $N=16$ spikes and $M=10$ realizations of the control strategy}
  \label{fig:targettrain_ol_highnoise}    
\end{center}
\end{figure}
